Semilattice Graphs for Distributed Databases

### 2022-10-03 paper/paper.tex
cleanup

      Let $L_0$ be an arbitrary semilattice. Now suppose we have:

      \begin{align*}
        (l_n, t_n) &: \mathrm{SemiFibration}(L_{n-1}) & \text{ for natural $n \geq 1$ } \\
        L_n &:= \mathrm{SemiTot}(L_{n-1}, l_n, t_n)    & \text{ for natural $n \geq 1$ }
      \end{align*}

@@

      We can further stack to higher ordinals than $\omega$. Let $n_u \geq 1$ be the number of universes. Let $L_{0, 0}$ be an arbitrary semilattice. Assume we have:

      \begin{align*}
        (l_{u, n}, t_{u, n}) &: \mathrm{SemiFibration}(L_{u, n-1}) & \text{for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u, n} &:= \mathrm{SemiTot}(L_{u, n-1}, l_{u, n}, t_{u, n})    & \text{ for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u+1, 0} &:= L_{u, \omega} & \text{ for natural $0 \leq u < n_u - 1$ }
      \end{align*}

>>>>

      Suppose we have:

      \begin{align*}
        L_0 &: \mathrm{Semilattice} & \\
        (l_n, t_n) &: \mathrm{SemiFibration}(L_{n-1}) & \text{ for natural $n \geq 1$ } \\
        L_n &:= \mathrm{SemiTot}(L_{n-1}, l_n, t_n)    & \text{ for natural $n \geq 1$ }
      \end{align*}

@@

      We can further stack to higher ordinals than $\omega$. Let $n_u \geq 1$ be the number of universes. Assume we have:

      \begin{align*}
        L_{0, 0} &: \mathrm{Semilattice} & \\
        (l_{u, n}, t_{u, n}) &: \mathrm{SemiFibration}(L_{u, n-1}) & \text{for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u, n} &:= \mathrm{SemiTot}(L_{u, n-1}, l_{u, n}, t_{u, n})    & \text{ for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u, 0} &:= L_{u-1, \omega} & \text{ for natural $1 \leq u < n_u$ }
      \end{align*}
